%==============================================================================
% File: 	introduction.Rnw
% Author: Peter DeWitt, peter.dewitt@ucdenver.edu
% Date:   9 November 2013
% 
% Purpose:	introduction section to the example data analysis report
%
% Change log:
% 13 November 2013 - file created
% 
%==============================================================================

\section{Introduction \label{sec:introduction}}

An example data analysis report.  The data set is fictitious.  Consider this work
only as an example of reproducible report writing.

\paragraph{Collaboration Considerations}

This report was authored in using R, {\tt knitr}, and  \LaTeX.  While there are
many advantages to authoring reports in \LaTeX, namely reproducible research via
literate programming, there are some disadvantages as well.  If the reader would
like the plain .tex files for reference and editing please let DeWitt know and
the files will be made available.  It is expected that the collaborators for
this project will be using Microsoft Office, or similar programs, to author
manuscripts, abstracts, and posters.  The text of this .pdf report should be
easy to copy and paste into Office type products.  However, the tables in this
document may not.  

To make the process of reproducing the tables presented in this document in a
Office type software package easier html versions of the tables have been
provided to the collaborators as well.  It is important to note that there are
two files, a .css file and a .html file, which need to be in the same directory
for the rendering of the .html tables to work.  Opening the .html file in any
web browser or may be imported directly into an Office program.  These tables
will require some formatting modifications.  

Graphics presented in this report are also sent to the collaborators as
individual .pdf files.  The graphics can be provided in any major graphics
format, size, and resolution as needed.  For example, if a file is needed as a
7~inch by 7~inch .tiff file with 1200 dpi resolution, please send such requests
to DeWitt and the graphics files will be produced as needed.  Many journals have
specific requirements for graphics and provide, via the journals' websites,
guidelines for authors.

%=============%
% end of file %
%=============%

